---
title: "linear model from Web"
author: "Jared Lobitana"
date: "7/19/23"
output:
   html_document:
         toc: true
         toc_depth: 5
        
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Read about the data from the website where it is staged.  Then form three regression models; Model1 is SIMS~ARM, Model2 is SIMS~GRIP, and Model3 is SIMS~ARM+GRIP. For each model find a 95% prediction interval of SIMS given a value of 94  for GRIP and 88 for ARM. Compare Model1 with Model3 using anova. Write it up in a markdown document, push the project up to your github account and submit it back to canvas as link. 

 


```{r include=FALSE}
require(tidyverse)
require(tigerstats)
require(rgl)
require(knitr)

```

```{r}
data <- read.csv(file="https://onlinestatbook.com/case_studies_rvls/physical_strength/data.txt",sep="",header=TRUE)  

```

# Introduction

We predict simulated a simulated strength score base on arm and grip strength. These 3 models will be found and compared upon one another. The response variable is numerical, and the explanatory variable is numerical, so we use the num-num helper file.



## Model 1 SIM~ARMS

## Results
### Graphical results

```{r}
model.1 <- lm(SIMS~ARM,data=data)
plot(SIMS~ARM,data=data)
abline(model.1, col='red')
```

This graph is showing that as the arm strength increases, the simulation follows. 

### Numerical results

```{r}
cor(SIMS~ARM,data=data)
```

The correlation is 0.69 which is showing that arm strength is related to  sim score. 

### Inferential  (Build model.1)

```{r}
model.1 <- lm(SIMS~ARM,data=data)
summary.lm(model.1)
```
Both the intercept and the coefficient of ARM strength are significantly different from 0 

### Prediction Interval

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.1, newdata, interval="predict")
```

The prediction interval is from -1.7 to 3.1 for SIM score. 


## Model 2 SIM~GRIP

## Results

### Graphical Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
plot(SIMS~GRIP,data=data)
abline(model.2, col='red')
```

This graph shows that the Grip strength goes up and the simulation goes up as well.The spread of the points around the regression line in the grip plot are more spread out than are strength plot.



### Numerical Results

```{r}
cor(SIMS~GRIP,data=data)
```

The correlation is 0.63 which shows that arm strength is related to sim score.


### Inferential Results

```{r}
model.2 <- lm(SIMS~GRIP,data=data)
summary.lm(model.2)
```

Both the intercept and the coefficient GRIP strength are significantly different from 0.

## Prediction Interval 

```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.2, newdata, interval="predict")
```

The prediction interval is from -3.1 to 2.0 for SIM score.


## Model 3 SIM~ARM+GRIP

## Results

### Numerical results (cor)

```{r}
cor(SIMS~ARM+GRIP,data=data)
```
  
The correlation is 0.73 which shows that Arm and Grip strength is related to sim score.

### Inferential  (Build 2-dimentional model.3)

```{r}
model.3 <- lm(SIMS~ARM+GRIP,data=data)
summary.lm(model.3)
```

As arm plus grip strength goes up, the simulation indicates that the sims will go up as well.

#### Predict Interval
```{r}
newdata = data.frame(ARM=88, GRIP=94)
predict(model.3, newdata, interval="predict")
```

The prediction interval is from -2.1 to 2.4 for SIM score.


## Comparing nested models ANOVA Test

### Model.1 vs Model.3
### Model.2 vs Model.3

## Informally compare Model.1 with model.2


```{r}
anova(model.3, model.1)
```

The p-value is .000000000149, Thus I reject the null hypothesis. Model three is smaller than model two as the rss for model three is smaller.
# Dicussion/ Conclusion

 Model 3 has the best between model 1 and model 2 because it has a smaller rss. To conclude, model 1 is better than model 2 however, we would need a smaller one, therefore model three is the best.
